---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(width = 80)
```
# growthscreener

<!-- badges: start -->
<!-- badges: end -->

The `growthscreener` package implements tools to evaluate child 
growth with respect to Dutch criteria for unusual growth. 
Application of these tools helps to identify children that meet 
criteria for criteria for referral from youth health care (JGZ) for
follow-up with a general physician or pediatrician.

The current version implements Dutch guidelines for

- height
- weight
- head circumference

## Installation

The following statements will install the `growthscreener` package

```{r eval = FALSE}
install.packages("remotes")
remotes::install_github("stefvanbuuren/growthscreener")
```

## Example

Find the advice for a very short girl:

```{r example}
library(growthscreener)

# a very short girl, 4 months old
msgcode <- calculate_advice_hgt(sex = "female", bw = 3250, ga = 40,
                                dob = as.Date("2018-07-31"),
                                dom1 = as.Date("2018-12-12"), 
                                y1 = 55)
msgcode
cat(fold(msg(msgcode)))

# some more details
d <- calculate_helpers(yname = "hgt", sex = "female", bw = 3250, ga = 40,
                       dob = as.Date("2018-07-31"),
                       dom1 = as.Date("2018-12-12"), 
                       y1 = 55)
unlist(d)
```

The height SDS at the age of about 4 months is equal to -3.255, which is 
the reason for referral.

## Background

The calculations implement several guidelines and guidelines:

- **JGZ-Richtlijn Lengtegroei 2019**: <https://www.ncj.nl/richtlijnen/alle-richtlijnen/richtlijn/lengtegroei-2019>
- **JGZ-Richtlijn Overgewicht 2012**: <https://www.ncj.nl/richtlijnen/alle-richtlijnen/richtlijn/overgewicht>
- **JGZ-Richtlijn Ondergewicht 2019**: <https://www.ncj.nl/richtlijnen/alle-richtlijnen/richtlijn/ondergewicht-2019>
- **Beslisboom Hoofdomtrek**: A decision tree for head circumference for children below the age of 1 year.

There are 43 different messages for height, 21 messages for weight and 15 messages for head circumference. To see them all:

```{r eval=FALSE}
messages
```



