---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(width = 80)
```
# growthscreener

<!-- badges: start -->
<!-- badges: end -->

The `growthscreener` package implements tools to evaluate child 
growth with respect to Dutch criteria for unusual growth. 
Application of these tools helps to identify children that meet 
criteria for criteria for referral from youth health care (JGZ) for
follow-up with a general physician or pediatrician.

Dutch guidelines for unusual height growth are currently implemented.

## Installation

The following statements will install the `growthscreener` package

```{r eval = FALSE}
install.packages("remotes")
remotes::install_github("stefvanbuuren/growthscreener")
```

## Example

Find the advice for a very short girl:

```{r example}
library(growthscreener)

# a very short girl, 4 months old
msgcode <- calculate_advice_hgt(sex = "F", etn = "N", 
                                bw = 3250, ga = 40,
                                dob = as.Date("2018-07-31"),
                                dom1 = as.Date("2018-12-12"), 
                                y1 = 55)
msgcode
cat(fold(msg(msgcode)))

# some more details
d <- calculate_helpers_hgt(sex = "F", etn = "N", 
                           bw = 3250, ga = 40,
                           dob = as.Date("2018-07-31"),
                           dom1 = as.Date("2018-12-12"), 
                           y1 = 55)
d
```

The height SDS at the age of 4 months is equal to -3.26, which is 
the reason for referral. There are 40 different messages for height.

## Background

The calculations follow to the "JGZ-Richtlijn Lengtegroei 2019". See
<https://www.ncj.nl/richtlijnen/alle-richtlijnen/richtlijn/lengtegroei-2019>
for more details.
